Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-02 manuscript.Rmd
new font does not have roman numerals

> Use five matches (Ⅰ Ⅰ Ⅰ Ⅰ Ⅰ) to form the number eight.

@@

1. The experimenter gives a hint that  the problem is easy to solve when using Roman numerals; if all students come up with the solution, she records it as evidence for the hypothesis.
2. The experimenter shows the solution "Ⅷ" and explains it; if all students come up with the solution, she records it as evidence for the hypothesis.
3. The experimenter does nothing; if all students come up with the solution, she records it as evidence for the hypothesis.

>>>>

> Use five matches (IIII) to form the number eight.

@@

1. The experimenter gives a hint that  the problem is easy to solve when using Roman numerals; if all students come up with the solution, she records it as evidence for the hypothesis.
2. The experimenter shows the solution "IX" and explains it; if all students come up with the solution, she records it as evidence for the hypothesis.
3. The experimenter does nothing; if all students come up with the solution, she records it as evidence for the hypothesis.
